Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-12-27 doc/JFLA2022/Slides/Slides.tex
Merge changes
add a slide on CI/CD

% \begin{frame}
%   \TODO{}{maintenance, CI/CD,  etc.   (several slides).}
% \end{frame}

@@

\begin{frame}
  \frametitle{Conclusion and perspectives}
  \begin{block}{}
    \begin{itemize}
    \item \Hydras wants to be a connection between scientific litterature and proof assistant technology:
      \begin{itemize}
      \item For the mathematician, it gives a concrete view of the mathematical contents: full proofs, examples, computable functions whenever possible, etc.
        \item  For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques.
      \end{itemize}
    \end{itemize}
  \end{block}
  \end{frame}

@@

\begin{frame}
  \frametitle{More TODOs}
  \begin{block}{}
    \begin{itemize}
    \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item etc.
    \item \Hydras and \community are on GitHub. Please contribute!
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)

      \end{itemize}
    \end{itemize}

>>>>

\begin{frame}
  \frametitle{Maintenance, CI/CD}
  \begin{block}{CD}
    The continuously evolving version of the book is continuously deployed from the master branch to the \community website.
  \end{block}

  \begin{block}{Reverse Dependencies Compatibility Testing}
    Since we have extracted part of {\color{plugincolor}goedel}, now {\color{plugincolor}goedel} depends on {\color{plugincolor}\Hydras}, and thus we are checking in CI that we do not break it (thanks to the \textcolor{lookcolor}{Coq Nix Toolbox},
    which can generate such CI workflows)
  \end{block}

  \begin{block}{}
  {\color{lookcolor}  With \Hydras, we hope to demonstrate that projects with complex dependencies are feasible to manage using recent advances in build management and infrastructure.}
  \end{block}

@@

\begin{frame}
  \frametitle{Conclusion and perspectives}
  \begin{block}{}
    \begin{itemize}
    \item \Hydras wants to provide  a connection between scientific litterature and proof assistant technology:
      \begin{itemize}
      \item For the mathematician, it gives a concrete view of the mathematical contents: full proofs, examples, computable functions whenever possible, etc.
        \item  For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques.
      \end{itemize}
    \end{itemize}
  \end{block}
  \end{frame}

@@

\begin{frame}
  \frametitle{More TODOs}
  \begin{block}{}
    \begin{itemize}
    \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item etc.
    \end{itemize}
  \end{block}

  \begin{block}{Call to contributors }
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. Please contribute!
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)
